A matrix-free approach for finite-strain hyperelastic problems using geometric multigrid

### 2018-09-04 doc/large_strain.tex
finite-strain
mention amg

    In this work, we advance the application of matrix-free approaches to problems in solid mechanics.
    We propose and numerically investigate different implementations of the finite-strain hyper-elastic tangent operator.
    In order to improve the convergence of iterative solvers, we also propose a way to construct level tangent operators
    and employ them to define a geometric multigrid preconditioner.
    Our implementation employs MPI and Intel Threading Building Blocks parallelization and SIMD vectorization.
    The performance of the matrix-free operator and the geometric multigrid preconditioner is compared to the matrix-based counterparts for a representative numerical example of heterogeneous hyper-elastic material in two and three dimensions.
  \end{abstract}

  \begin{keyword}
      adaptive finite element method \sep
      geometric multigrids \sep
      large strain \sep
      matrix-free \sep
      hyperelasticity
  \end{keyword}

>>>>

    In this work, we advance the application of matrix-free approaches to problems in solid mechanics.
    We propose and numerically investigate different implementations of the finite-strain hyper-elastic tangent operator.
    In order to improve the convergence of iterative solvers, we also propose a way to construct level tangent operators
    and employ them to define a geometric multigrid preconditioner.
    Our implementation employs MPI and Intel Threading Building Blocks parallelization and SIMD vectorization.
    The performance of the matrix-free operator and the geometric multigrid preconditioner is compared to the matrix-based implementation with an algebraic multigrid preconditioner for a representative numerical example of heterogeneous hyper-elastic material in two and three dimensions.
  \end{abstract}

  \begin{keyword}
      adaptive finite element method \sep
      geometric multigrids \sep
      finite-strain \sep
      matrix-free \sep
      hyperelasticity
  \end{keyword}
